---
title: "Interactive visualize mapping - a case study in Vietnam"
author: "Tung Trinh"
date: "April 16, 2017"
output: html_document
---

#**Introduction**

In 2014, Vietnam was under a big measles outbreak which led to more than 15,033 confirmed case [(Data from National Institute of Hygiene and Epidemiology)](www.nihe.org.vn) and 146 fatalites national wide [[1]](http://wwwnc.cdc.gov/eid/article/22/4/15-1595_article). Most of severe cases who required hospitalization were unvaccinated children. In order to investigate the measles outbreak, we conducted serological experiment to observe the immunity status in the population of four cities which has more than one million population. In additon, by seeing the vaccine coverage of the population, the reason why measles outbreak could spread uncontrolable can be answered. 

This shiny application is a supplemental data to support our study, you can access by following this [link](http://oucru-nihe.ddns.net:3838/). It demonstrates the vaccine coverage from 2000 to 2014 with the population information and this README file helps you build up a similar shiny app. If you have any question, please email to **[me](mailto:tung.trson@gmail.com)**. **ALL DATA USED IN THIS SHINY ARE BELONG TO the Epidemiology department of National Institute of Hygiene and Epidemiology and Oxford University Clinical Research Unit - Hanoi. 
© Oxford University Clinical Research Unit - Hanoi and National Institute of Hygiene and Epidemiology

#**Package Usage**
This shiny app using **leaflet** package, a neat and fancy map visualization, along with **plotly** package, another fancy visualize package for plotting. 

```{r, echo=FALSE, message= F , warning= F}
#Loading nessasry packages
library(dplyr) #data manuplation 
library(leaflet) #interative map
library(flexdashboard) #ready-to-use template 
library(shiny) # shiny application built package
library(plotly) # interactive plot
```

#**Data**
```{r, echo=F, message=F , warning =F}
#Data loading
thinnedvn <- readRDS("data/vietnam.rds")
# thinnedvn <- readRDS("data/thinnedvietnam.rds")
nat.vaccov <- readRDS("data/national_vaccov.rds")
vietpop <- readRDS("data/viet_pop.rds")
ave.vac <- readRDS("data/ave_vac.rds")
```

#**Additional self-built function**
```{r, echo = F , message= F , warning = F}
#Data sorting function
sort_data <- function(year = 2001){
  tmp <- grep(year,colnames(nat.vaccov))
  dat.<- nat.vaccov[,c(1,tmp)]
  colnames(dat.) <- c("province","coverage")
  dat.$coverage <- dat.$coverage*100
  dat.$grp <- cut(dat.$coverage, breaks = c(0, 50, 60,70,80,90,95,100), labels = c("<50", "50-60","60-70","70-80","80-90","90-95","95-100"))
  thinnedvn@data<- left_join(thinnedvn@data,dat.)            
  return(thinnedvn)  
}

fil <- function(x){x
  x[which(x > 0.1 | x <= 1)]
}
```

Vaccine Coverage
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Geographical first dose of Measle Vaccine Coverage
Vaccine Coverage
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Geographical first dose of Measle Vaccine Coverage

```{r}
#Leaflet map 
output$map <- renderLeaflet({
  map <- get_data()
  fac_col <- colorFactor(c("#ffffb2","#fed976","#feb24c","#fd8d3c","pink","#bd0026", "#800026"),thinnedvn@data$grp)
  leaflet(map) %>%
    addProviderTiles('CartoDB.Positron') %>%
    clearShapes() %>%
    addPolygons(stroke = T , smoothFactor = .1 , fillOpacity = .5, color = ~fac_col(grp), layerId = ~province) %>%
    addLegend("bottomleft", pal = fac_col, value  = ~grp, opacity = .5, title = "Coverage of 1st dose of measles vaccine")
})

#Click Event
click_tract <- eventReactive(input$map_shape_click, {
  
  x <- input$map_shape_click
  y <- x$id
  # print(x)
  return(y)
  # print(y)
  # return(names(x))
})

observe({
  # print("clicked!")
  # print(click_tract())
  req(click_tract()) # do this if click_tract() is not null
  # Add the clicked tract to the map in aqua, and remove when a new one is clicked
  
  
  map <- leafletProxy('map') %>%
    removeShape('dat') %>%
    addPolygons(data = thinnedvn[thinnedvn$province == click_tract(), ], fill = FALSE,
                color = 'lightblue', opacity = 1, layerId = 'dat')
})

prov_pop <- reactive({
  return(vietpop[vietpop$province == click_tract(),])
})

pro_vac <- reactive(({
  return(nat.vaccov[nat.vaccov$province == click_tract(),])  
}))

leafletOutput('map')
```

Column {data-width=500}
-----------------------------------------------------------------------

### Province|City Information 

```{r}
output$info <- renderUI({
  info <- paste("Province|City:",click_tract(),sep = " ")
  pop <- paste("Population:",prov_pop()$population,"people",sep = " ")
  area <- paste("Area:", prov_pop()$area,"km square", sep =" ")
  density <- paste("Population density:",prov_pop()$population_density,"person/km square", sep =" ")  
  # tmp <- paste(info, pop, area , density)
  HTML(paste(info, pop , area, density, sep="<br/>"))
})

htmlOutput("info")

```

### Time-series Vaccine Coverage 

```{r}
output$plotly <- renderPlotly({
  prov <- as.numeric((pro_vac()[,-1]*100))
  ave.vac <- data.frame(ave.vac,prov)
  plot_ly(data = ave.vac, x = ~time_vector, y = ~ave.cov, name = "National average coverage", mode = "lines" , line = list(color = "black", width = 4)) %>%
    add_trace(y = ~ ave.cov, name = "National average coverage",line = list(color = "red", width = 4)) %>%
    add_trace(y = ~ south_ave, name = "Southern average coverage",  line = list(color = "pink", width = 4 )) %>%
    add_trace(y = ~ north_ave, name = "Northern average coverage", line = list(color = "blue", width = 4 )) %>%
    add_trace(y = ~ central_ave, name = "Central average coverage", line = list(color = "green", width = 4)) %>%
    add_trace(y = ~ prov, name = paste("Coverage of",click_tract(), sep = " "), line = list(color = "black", width = 4)) %>%
    layout(title = "Coverage of Measles first dose vaccine",
           xaxis = list(title = "Year"),
           yaxis = list (title = "Coverage (Percent)"))
})

plotlyOutput("plotly")
```

